### 2018-07-28 paper/article.tex
Summary.
Corrections.

\documentclass[pmlr]{jmlr}
\input{_head}
%TODO: Max 14 pages
%TODO: No personal information or reference to the authors should be introduced in the submitted paper.
%TODO: Submissions will be evaluated concerning their technical quality, relevance, significance, originality and clarity.

@@

Following work focuses on the binary classification of the highly imbalanced problems, with an \textsc{ir}(\emph{imbalanced ratio}) greater than \oldstylenums{9}, which is an important issue not only in the context of the construction of appropriate models, but even in a proper quality measurement \citep{Elazmeh:2006}. One of the important problems is also the fact that the number of patterns in the \emph{minority class} may be so small that it will not allow to achieve the appropriate discriminatory power of the model, which may lead to its \emph{overfitting} \citep{Chen:2008}. Most of these problems are the subject of extensive research \citep{Bunkhumpornpat:2009,Chawla:2002}.

@@

\begin{figure}[!h]
\floatconts
  {fig:preproc}
  {\caption{Examples of data preprocessing methods.}}
  {%
    \subfigure[Original dataset]{\label{fig:overs}%
    \includegraphics[clip=true, width=.25\linewidth,
    				 trim = 11 141 141 11]
    {figures/preprocessing}}%
    \qquad
    \subfigure[\textsc{smote}]{\label{fig:smote}%
    \includegraphics[clip=true, width=.25\linewidth,
    				 trim = 141 141 11 11]
    {figures/preprocessing}}%

@@

\paragraph{Extending pool with oversampling} As an extension of the method of classifier ensemble construction, it is also proposed to extend its pool by a model learned on an additional data set, which is a full set of data subjected to \emph{oversampling}. It is worth testing if the knowledge gained from this method may be a valuable contribution to the ensemble decision. Due to impossibility of using \textsc{smote} or \textsc{adasyn} for oversampling the minority class with only few instances, only its basic variant will be employed.

@@

There are two groups of solutions here. The first are based on component \emph{decisions} of the committee, most often employing the \emph{majority voting} to produce a final decision. The decision rules proposed in this work are, however, part of the second group, where the \emph{fuser} is carried out by \emph{averaging} (or \emph{accumulating}) the \emph{support vectors} received from the members of a pool.

\begin{note}
It should be remembered that in such methods, it is necessary to use a \emph{probabilistic classification model}, which also requires \emph{quantitative} and not \emph{qualitative data}.
\end{note}

Five fusers were proposed:

@@

In order to reward classifiers with greater \emph{"certainty"} for given object, the decision for each pattern is weighted by the absolute difference between class support, for the needs of research called the \emph{contrast}. Individual classifiers in the pool do not have to be better or worse for each of the tested patterns. This is illustrated in Figure \ref{fig:contrast}, where we can see two cases of ensembles. There are tested patterns on the X axis and classifiers in the pool on the Y axis. A white square means the \emph{contrast} of 1, and therefore a \emph{sure} decision, and the black square the \emph{contrast} of 0, which describes the pattern that is exactly on the decision boundary.

@@

	\item \textbf{\textsc{nci}} --- accumulation by a product of normalized weights \textbf{\textsc{nor}} and a \emph{contrast} \textbf{\textsc{con}}.
\end{enumerate}

The proposed method of constructing the committee makes its size directly dependent on the \textsc{ir}, which, given the highly unbalanced data (for example with \textsc{ir} greater than 40), leads to the construction of an extensive hybrid model. Therefore, the method of prunning it to a smaller size was also considered.

@@

In the proposed method, using the signed-rank test, we are \emph{clustering} the pool of $k$ (or $k+1$ on the \emph{oversampling} variation of a method) classifiers to $n$ groups (where $n\leq k$), to average the support and weight classes within groups to create a new set of supports from $s'_1$ to $s'_n$, passed later on to \emph{fuser}.

@@

\begin{note}
In the considered case of pruning, we ignore the possible situation in which the answer $\Psi_1$ is dependent on $\Psi_2$, the answer $\Psi_2$ is dependent on $ \Psi_3$, but $\Psi_1$ is not dependent on $\Psi_3$. This is an interesting issue that will be addressed in future research, but to simplify the proposal, a simplified approach has been used.
\end{note}

@@

For the experimental evaluation of the proposed method, a collection of datasets made available with \textsc{keel} \citep{alcala2011keel} was used, focusing on a section containing highly unbalanced data, with \textsc{ir} greater than 9 \citep{fernandez2009hierarchical}. From among the available datasets, \oldstylenums{40} were selected presenting only binary problems with quantitative attributes. A review of selected datasets, including information on their number of features, the number of patterns in each class and the unbalance ratio is presented in Table \ref{tab:datasets}.

@@

As may be observed in the summary, the experiments are based on datasets with relatively small spatiality (up to \oldstylenums{13} dimensions), with imbalance ratio from \oldstylenums9 to even \oldstylenums{40}. The datasets provided by \textsc{keel}, to ensure easy comparison between results presented in various research, are already pre-divided into five parts, which forces the use of \emph{k-fold cross-validation} with $k = 5$ in experiments \citep{alpaydin2009introduction}.

@@

To provide a comparative result for the method presented in the following paper, each base classifier was also tested for the raw, imbalanced dataset and its under- and oversampled versions. Undersampling, due to high instability of results, was repeated five times on each fold. Used statistical analysis tool was a paired dependency between the classifier, which achieved the highest result and each of the others, calculated using the signed-rank \emph{Wilcoxon} test \citep{wilcoxon1945individual}.

The full implementation of the proposed method, content of the following paper and the script allowing the repetition of the presented research may be found in the git repository\footnote{\url{https://github.com/w4k2/umce}}.

@@

The results of the conducted research, for individual base classifiers, are presented in Tables 2 and 3. They were divided to present in individual sections a \emph{balanced accuracy} achieved by particular variations of the method proposed in the following paper. In the first division stage, we show the impact of inclusion of the classifier built on the \emph{oversampled} dataset, in the second, the use of the proposed pruning method, and in the third -- employed \emph{fuser}. This gave 20 variations of the algorithm.

@@

%\begin{sidewaystable}
%	\restable{kNN}{k\textsc{nn}}
%\end{sidewaystable}

@@

As we can see in Table 2, which presents the quality of classification using the \textsc{gnb} algorithm, there were only two datasets, where the lone best solution was to train the model on a full, imbalanced dataset, and one where the best solution were simple \emph{over-} or \emph{undersampling}. In the Table 3, showing the results for the \textsc{dtc} classifier, we are dealing with a similar situation in which, however, \emph{undersampling} never turns out to be the best in the tested pool of solutions.

A clearer interpretation of the results may take place after the analysis of the Table 4, showing a summary of the results achieved by individual variations of the proposed method, presenting the number of datasets for which a given variation took part in the construction of the best solution.

\begin{table}[!h]
%\vspace{-.5em}
\centering
\centering
\setlength{\tabcolsep}{3.5pt}
\def\arraystretch{1.1}
\begin{tabular}{@{}|l|ccc||cc|cc|ccccc|@{}}\hline%

@@

	\csvreader[head to column names,
	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
	           late after last line = \\\hline]
	{summary.csv}{}%
	{\clf &
	\full & \us & \os &
	\withoutos & \withos & 
	\withoutpru & \withpru &
	\reg & \wei & \con & \nor & \nci

	}%
\end{tabular}
\caption{Final summary of proposed method variations. %Values in cells are numbers of datasets, in which method reached the best score, or have been statistically dependent to the best score. 
\\\emph{(OSE -- extending pool by oversampled dataset, Pru. -- usage of pruning)}}\label{tab:summary}
\vspace{-2em}
\end{table}

@@

%%%
%%% Acknowledgements and references
%%%
\acks{
	---\\
	---\\
	---
	%This work was supported by the Polish National Science Center under the grant no. UMO- 2015/19/B/ST6/01597 and by the statutory fund of the Faculty of Electronics, Wroclaw University of Science and Technology.
}
\bibliography{bibliography}

>>>>

\documentclass[pmlr]{jmlr}
\input{_head}

@@

Following work focuses on the binary classification of the highly imbalanced problems, with an \textsc{ir} (\emph{imbalanced ratio}) greater than \oldstylenums{9}, which is an important issue not only in the context of the construction of appropriate models, but even in a proper quality measurement \citep{Elazmeh:2006}. One of the important problems is also the fact that the number of patterns in the \emph{minority class} may be so small that it will not allow to achieve the appropriate discriminatory power of the model, which may lead to its \emph{overfitting} \citep{Chen:2008}. Most of these problems are the subject of extensive research \citep{Bunkhumpornpat:2009,Chawla:2002}.

@@

\begin{figure}[!h]
\floatconts
  {fig:preproc}
  {\caption{Examples of data preprocessing methods.}}
  {%
    \subfigure[Original dataset / Oversampling]{\label{fig:overs}%
    \includegraphics[clip=true, width=.25\linewidth,
    				 trim = 11 141 141 11]
    {figures/preprocessing}}%
    \qquad
    \subfigure[\textsc{smote}]{\label{fig:smote}%
    \includegraphics[clip=true, width=.25\linewidth,
    				 trim = 141 141 11 11]
    {figures/preprocessing}}%

@@

\paragraph{Extending pool with oversampling} As an extension of the method of classifier ensemble construction, it is also proposed to expand its pool by a model learned on an additional data set, which is a full set of data subjected to \emph{oversampling}. It is worth testing if the knowledge gained from this method may be a valuable contribution to the ensemble decision. Due to impossibility of using \textsc{smote} or \textsc{adasyn} for oversampling the minority class with only few instances, only its basic variant will be employed.

@@

There are two groups of solutions here. The first are based on component \emph{decisions} of the committee, most often employing the \emph{majority voting} to produce a final decision. The decision rules proposed in this work are, however, part of the second group, where the \emph{fuser} is carried out by \emph{averaging} (or \emph{accumulating}) the \emph{support vectors} received from the members of a pool. It should be remembered that in such methods, it is necessary to use a \emph{probabilistic classification model}, which also requires \emph{quantitative} and not \emph{qualitative data}, so we need to reject classification algorithms such as \emph{Support Vector Machines}, whose probabilistic interpretation becomes reliable only in cases of large training sets.

Five accumulative fusers were proposed to analyze:

@@

In order to reward classifiers with greater \emph{"certainty"} for given object, the decision for each pattern is weighted by the absolute difference between class support, for the needs of research called the \emph{contrast}. Individual classifiers in the pool do not have to be better or worse for each of the tested patterns. This is illustrated in Figure \ref{fig:contrast}, where we can see two cases of ensembles. There are tested patterns on the \emph{X} axis and classifiers in the pool on the \emph{Y} axis. A white square means the \emph{contrast} of 1, and therefore a \emph{sure} decision, and the black square the \emph{contrast} of 0, which describes the pattern that is exactly on the decision boundary.

@@

	\item \textbf{\textsc{nci}} --- accumulation weighted by a product of normalized weights and a \emph{contrast}.
\end{enumerate}

The proposed method of constructing the committee makes its size directly dependent on the \textsc{ir}, which, given the highly unbalanced data (for example with \textsc{ir} greater than \oldstylenums{40}), leads to the construction of an extensive hybrid model. Therefore, the method of prunning it to a smaller size was also considered.

@@

In the proposed method, using the signed-rank test, we are \emph{clustering} the pool of $k$ (or $k+1$ on the \emph{oversampling} variation of a method) classifiers to $n$ groups (where $n\leq k$), to average the support and weight classes within groups to create a new set of supports from $s'_1$ to $s'_n$, passed later on to \emph{fuser}. It is important to denote, that in the considered case of pruning, we ignore the possible situation in which the answer $\Psi_1$ is dependent on $\Psi_2$, the answer $\Psi_2$ is dependent on $ \Psi_3$, but $\Psi_1$ is not dependent on $\Psi_3$. This is an interesting issue that will be addressed in future research, but to clarify the proposal, a simplified approach has been used.

@@

@@

For the experimental evaluation of the proposed method, a collection of datasets made available with \textsc{keel} \citep{alcala2011keel} was used, focusing on a section containing highly unbalanced data, with \textsc{ir} greater than \oldstylenums{9} \citep{fernandez2009hierarchical}. From among the available datasets, \oldstylenums{40} were selected, presenting only binary problems with quantitative attributes. A review of selected datasets, including information on their number of features, the number of patterns in each class and the imbalance ratio is presented in Table \ref{tab:datasets}.

@@

As may be observed in the summary, the experiments are based on datasets with relatively small spatiality (up to \oldstylenums{13} dimensions), with imbalance ratio from \oldstylenums9 to even \oldstylenums{40}. The datasets provided by \textsc{keel}, to ensure easy comparison between results presented in various research, are already pre-divided into five parts, which forces the use of \emph{k-fold cross-validation} with \oldstylenums{5} folds in experiments \citep{alpaydin2009introduction}.

@@

To provide a comparative result for the method presented in the following paper, each base classifier was also tested for (\emph{i}) the raw, imbalanced dataset and its (\emph{ii}) under- and (\emph{iii}) oversampled versions. Undersampling, due to high instability of results, was repeated five times on each fold. Used statistical analysis tool was a paired dependency between the classifier, which achieved the highest result and each of the others, calculated using the signed-rank \emph{Wilcoxon} test \citep{wilcoxon1945individual}.

The full implementation of the proposed method, content of the following paper and the script allowing to reconstruct the presented research may be found in the \emph{git} repository\footnote{\url{https://github.com/w4k2/umce}}.

@@

The results of the conducted research, for individual base classifiers, are presented in Tables \ref{tab:GNB} and \ref{tab:DTC}. They were divided to present in individual sections a \emph{balanced accuracy} achieved by particular variations of the method proposed in the following paper. In the first division stage, we show the impact of inclusion of the classifier built on the \emph{oversampled} dataset, in the second, the use of the proposed \emph{pruning} method, and in the third -- employed \emph{fuser}. It gave the number of \oldstylenums{20} algorithm variations.

@@

@@

As we can see in Table \ref{tab:GNB}, which presents the quality of classification using the \textsc{gnb} algorithm, there were only two datasets, where the lone best solution was to train the model on a full, imbalanced dataset, and one where the best solution were simple \emph{over-} or \emph{undersampling}. In the Table \ref{tab:DTC}, showing the results for the \textsc{dtc} classifier, we are dealing with a similar situation in which, however, \emph{undersampling} never turns out to be the best in the tested pool of solutions.

A clearer interpretation of the results may take place after the analysis of the Table \ref{tab:summary}, showing a summary of the results achieved by individual variations of the proposed method, presenting the number of datasets for which a given variation took part in the construction of the best solution.

\begin{table}[!h]

\centering
\centering
\setlength{\tabcolsep}{3.5pt}
\def\arraystretch{1.1}
\begin{tabular}{@{}|l|ccc||cc|cc|ccccc|@{}}\hline%

@@

	\csvreader[head to column names,
	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
	           late after last line = \\\hline]
	{summary.csv}{}%
	{\clf &
	\full & \us & \os &
	\withoutos & \withos & 
	\withoutpru & \withpru &
	\reg & \wei & \con & \nor & \nci
	}%

\end{tabular}
\caption{Final summary of proposed method variations. %Values in cells are numbers of datasets, in which method reached the best score, or have been statistically dependent to the best score. 
\\\emph{(OSE -- extending pool by oversampled dataset, Pru. -- usage of pruning)}}\label{tab:summary}
\label{tab:summary}
\end{table}

@@

%%%
%%% Acknowledgements and references
%%%
\acks{
	This work was supported by the Polish National Science Center under the grant no. UMO- 2015/19/B/ST6/01597 and by the statutory fund of the Faculty of Electronics, Wroclaw University of Science and Technology.
}
\bibliography{bibliography}
